Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
table  updates

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
\hline
$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
\hline
$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
\hline
$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
\hline
\end{tabular}
\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}. All the covariates are statistically useful to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
\label{table:spot.test}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.00063$    & $2e-16$  & $1.42e-09$ \\
\hline
$\beta_{1}$            &    $2e-16$    & $2e-16$  & $2e-16$ \\
\hline
$\beta_{2}$            &     $2e-16$   & $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.067$   &  $0.40$  & $0.38$\\
\hline
$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
K            &     $2e-16$   &  $2e-16$   & $2e-16$ \\
\hline
P            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
\hline
$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
\hline
$\text{Residuals}$      &     $0.71 \ms$    &  $ 0.66 \ms$ & $0.70 \ms$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction.overall}. All the parameters are statistically helpful to address spurious variations in RV's except the FWHM. Concerning the keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet. Note that since non linear least squares are required, the residual standard error rather than the $R^2$ is displayed for each case.}
\label{table:spotplanet.test}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
\hline
$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
\hline
$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
\hline
$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
\hline
\end{tabular}
\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated RVs from spurious variations caused by a spot. 
All the covariates are statistically significant to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF.
The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs. \jessi{Isn't the width of the CCF parameter sig for N mean RV at 0.017?  Previously it was noted that a 5\% significance level was going to be used.}}
\label{table:spot.test}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.00063$    & $2e-16$  & $1.42e-09$ \\
\hline
$\beta_{1}$            &    $2e-16$    & $2e-16$  & $2e-16$ \\
\hline
$\beta_{2}$            &     $2e-16$   & $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.067$   &  $0.40$  & $0.38$\\
\hline
$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
K            &     $2e-16$   &  $2e-16$   & $2e-16$ \\
\hline
P            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
\hline
$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
\hline
$\text{Residuals}$      &     $0.71 \ms$    &  $ 0.66 \ms$ & $0.70 \ms$  \\
\hline
\end{tabular}
\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction.overall} to correct the estimated RVs from spurious variations caused by a spot while also accounting for a true planet RV. 
All the covariates are statistically significant to explain the variability in RV's caused by a spot, except the FWHM.
Concerning the Keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.
}
\label{table:spotplanet.test}
\end{table}
